Exploratory Plots

### 2020-05-28 exploratory/2020/README.Rmd
Plot fraction of reads mapped

```{r fit_db_sensspec}
sensspec <- read_tsv(here('subworkflows/2_fit_reference_db/results/merged.sensspec')) %>% 
  relevel_method()
sensspec %>% 
  plot_jitter(mcc)
```

@@

>>>>

```{r fit_db_sensspec}
sensspec <- read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.txt')) %>% 
  relevel_method()
sensspec %>% 
  plot_jitter(mcc)
```

@@

```{r fraction_reads_mapped}
df_fraction_mapped <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.txt'))
df_fraction_mapped %>% 
  ggplot(aes(dataset, fraction_mapped)) +
  geom_jitter()
```
